Additional Tables

### 2019-06-12 notebooks/article_notebook2.Rmd
corrected for wrong excluded isolate

```{r Import data, message=FALSE, warning=FALSE}
# Vector of excluded samples
ex_samples <- c(
  "2016-17-565-1-S",
  "2016-02-415-2-S",
  "2016-02-428-2-S",
  "2016-02-486-2-S",
  "2016-02-732-2-S"
  )

>>>>

```{r Import data, message=FALSE, warning=FALSE}
# Vector of excluded samples
ex_samples <- c(
  "2016-17-565-1-S",
  "2016-02-428-2-S",
  "2016-02-486-2-S",
  "2016-02-732-2-S",
  "2014-01-1741-1-S"
  )
